\section{Course Pages}

The main aspects that the features of the course pages that will be analysed and discussed are:
\begin{itemize}
    \item Functional Requirements - have the features outlined been completed?
    \item Non-functional Requirements - how well do the features complete their objectives?
    \item Usability Tests - how do users utilise the features and what do they think of it?
\end{itemize}

\subsection{Functional Requirements}
As stated before, there were a total of 14 functional requirements. Within these requirements there were 6 high priorty requirements, 3 medium priority requirements and 5 low priority requirements.
In total only 9 of the functional requirements were completed. The 5 features that were not complete due to being low priority. There were also 

\title{Completed}
\begin{itemize}
    \item Users can click on the links in the sidebar to be directed to the corresponding component;
    \item Users can view the announcments within the dashboard;
    \item Users can view the course content;
    \item Administrators of the course can create announcments within the dashboard;
    \item Users can make comments on announcments;
    \item Administrators can upload the course outline onto the course outline page;
    \item Users can download the course content;
    \item Administrators can edit the sidebar to change what components are linked;
    \item Course content is catergorised based on how the content is catergorised in the topic tree;
    \item Administrators can edit the announcements made in the dashboard;
    \item Users can intereact with widgets to enchance their experience with the LMS;
    \item Users can toggle on or off specific widgets.
\end{itemize}

\title{Uncompleted}
\begin{itemize}
    \item Users can view the course outline of a course;
    \item Administrators can add course content into the page by selecting content from the topic tree;
    \item Administrators can upload the course outline onto the course outline page;
    \item Administrators can edit the sidebar to change what components are linked;
    \item Users can toggle on or off specific widgets.
\end{itemize}

The course outline feature was removed from the final design as it was not highly prioritised and other features being prioritised. 
The feature for administrators to add course content onto a course was streamlined, so that administrators can add content on the topic tree and have those changes be reflected on the course content page.
The last feature that was not complete was the functionality of allowing users to toggle on or off specific widgets. This was due to the lack of priority for this feature and thus was not implemented.\\

Apart from the outlined requirements, there were also other functionality that were introduced:
\begin{itemize}
    \item Users can view the courses that they are enrolled in;
    \item Users can select a course that they would want to view the course pages for;
    \item Users can view the most recent announcement;
    \item Users can view the progress of their courses;
\end{itemize}

These functional features were added early in Thesis B as they are the features that would make up the course selection page.

\subsection{Non-Functional Requirements}
The non-functional requirements that will be used to analyse the course pages are:
\begin{itemize}
    \item Performance;
    \item Responsiveness;
    \item Scalability.
\end{itemize}

\subsubsection{Performance}

\subsubsection{Responsiveness}

\subsubsection{Scalability}

\subsection{Usability Tests}
