\section{Forums}

As mentioned in the project approach, the main goal of the forums component is for it to be the central location for conversation and discussion between students and educators for each course.
The aim was to implement all the required and desired features into the LMS' forum so that staff would no longer have to turn to a third-party forum services.
Aside from the standard features of viewing and adding posts, comments and replies, the additional features built that helped contribute to this goal include:

\begin{itemize}
    \item Advanced search, filtering and sorting capabilities to assist in finding specific posts;
    \item Methods for both students and staff to assist in bringing attentions to posts, like upvoting, endorsing and pinning posts; and,
    \item The ability to copy a direct link to a post to assist in sharing.
\end{itemize}

\subsection{What Would You Have Done Differently?}

If this project were to be re-done, the main thing that would've been done differently is conducting more research on different third-party libraries instead of going ahead with the first one found.
For React in particular, there are many third-party packages that essentially provide the same service but with different features.
Researching would allow for the package with the most desired features to be chosen.
Choosing a package with sufficient documentation could also prevent developers from wandering around in the dark when trying to implement it into the project.
Overall, choosing the correct package from the start would've prevented a lot of refactoring of the code, therefore saving time in the development process and allowing more features to be built on time.

\subsection{Future Work}
Future work for the forums component includes:

\begin{itemize}
    \item Ability to attach documents and files to posts;
    \item Ability to add attachments to replies and comments;
    \item More share options so that links can be shared directly to other platforms;
    \item Introduce natural language processing to parse post titles and descriptions as they are being written and generate suggested tags; and,
    \item Advanced querying that searches existing posts as users type out titles and descriptions and suggests similar posts to reduce duplicates.
\end{itemize}